---
title: "Work for Dan"
author: "Matthew Reardon"
date: "Friday, January 28, 2016"
output: html_document
---
</br>
First we will read in the segment information and the sites from Dan's csv.
</br>
```{r}
#bring in dan's segs and stations
dan_work<-read.csv('C:\\Users\\MReardon\\Desktop\\dan_Seg_Work.csv')
```

Load the neccessary libraries and the fnList function from user 42 from stackoverflow. The fnlist function outputs a list to file while keeping the names of a list.
</br>

```{r include=TRUE, cache=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(knitr)
library(data.table)

#function from stackoverlow, user "42", http://stackoverflow.com/questions/8261590/write-list-to-a-text-file-preserving-names-r
fnlist <- function(x, fil){ z <- deparse(substitute(x))
                         cat(z, "\n", file=fil)
                         nams=names(x) 
                   for (i in seq_along(x) ){ cat(nams[i], "\t",  x[[i]], "\n", 
                                            file=fil, append=TRUE) }
                         }

```

Arrange by Segment ID.
</br>

```{r include=TRUE, cache=FALSE}
dan_work<-arrange(dan_work, Segment)
```
Look at the "dan_work" file. Note multiple Final.Text values per segment.  These are the stations on each segment.
```{r}
head(dan_work)
```

Use tapply.  This runs the paste function on the "Final.Text" column (first parameter) and uses the "segment" column as the ID or groupby variable.
</br>

```{r include=TRUE, cache=FALSE}
a<-tapply(dan_work$Final.Text, dan_work$Segment, function (x) paste(x))
```
Look at the list that is output.  We need to put the list with its names into a text file.
```{r include=TRUE, cache=FALSE}
head(a)
```

Finally using fnlist function, output to text file.
```{r include=TRUE, cache=FALSE}
fnlist(a, "C:\\Users\\MReardon\\Desktop\\test.txt")
```

Fin.




